Probabilistic forecasting of hourly Emergency Department arrivals

### 2022-02-10 paper/paper.Rmd

```{r Skill-rel2bench, fig.cap= "Pinball skill score for the seven best performing approaches.", fig.align='center',out.width= "100%"}
```

@@

```{r time-accuracy, fig.cap= "Speed (Running time) vs. forecast accuracy", fig.align='center',out.width="70%"}
```

>>>>

<!--
```{r Skill-rel2bench-reduced, fig.cap= "Pinball skill score for the seven best performing approaches.", fig.align='center',out.width= "70%"}
```

@@

```{r time-accuracy, fig.cap= "Running time vs. forecast performance", fig.align='center',out.width= "70%"}
```
